---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# tscompdata

[![Pending Pull-Requests](http://githubbadges.herokuapp.com/robjhyndman/tscompdata/pulls.svg?style=flat)](https://github.com/robjhyndman/tscompdata/pulls)

The R package *tscompdata* provides time series data from the following forecasting competitions: M, M3, NN3, NN5, NNGC1, Tourism and GEFCom2012.

The M, M3 and Tourism data are loaded from the Mcomp and Tcomp packages. The remaining data are contained within the tscompdata package.

## Installation

You can install the **development** version from [Github](https://github.com/robjhyndman/tscompdata) with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("robjhyndman/tscompdata")
```

## Usage

```{r nn5}
library(tscompdata)
library(forecast)
library(ggplot2)
autoplot(nn5[[23]])
```

## License

This package is free and open source software, licensed under GPL-3.
