---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "READMEfigs/",
  cache = TRUE
)
```

# tscompdata

[![Pending Pull-Requests](http://githubbadges.herokuapp.com/robjhyndman/tscompdata/pulls.svg?style=flat)](https://github.com/robjhyndman/tscompdata/pulls)

The R package *tscompdata* provides time series data from the following forecasting competitions: M, M3, NN3, NN5, NNGC1, Tourism, GEFCom2012, GEFCom2014 and GEFCom2017,  along with some tools for plotting the data.

The M, M3 and Tourism data are loaded from the Mcomp and Tcomp packages. The remaining data are contained within the tscompdata package.

## Installation

You can install the **development** version from [Github](https://github.com/robjhyndman/tscompdata) with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("robjhyndman/tscompdata")
```

## Usage

```{r nn5}
library(tscompdata)
library(forecast)
library(ggplot2)
autoplot(nn5[[23]])
```

## License

This package is free and open source software, licensed under GPL-3.
